\documentclass[aps,rmp,preprint,superscriptaddress,10pt,onecolumn]{article}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{enumerate}
\usepackage{color}
\usepackage{caption}
\usepackage[final]{hyperref}
\usepackage{fontspec}
%\usepackage{natbib}
%\bibliographystyle{plainnat}


\setmainfont{Times New Roman}
% \usepackage{unicode-math}
% \setmathfont{XITS Math}


%\setlength{\parindent}{20pt}
\def\thesubsectiondis{\unskip\arabic{subsection}}
 
\begin{document}

\title{Data summary:\\\textit{Growth: From Microorganisms to Megacities}, Vaclav Smil (2019)}
\author{Liam P. Shaw}
\date{\today}


\maketitle

\section*{Summary}

\noindent This document contains graphs fitted from a variety of datasets in \textit{Growth} by Vaclav Smil (2019). Code and data to reproduce analysis are available at \url{https://github.com/liampshaw/Smil-Growth-2019}. Figure captions and page numbers are taken from the printed version of the book, first edition.

\par Thanks to Vaclav Smil for sharing these datasets to make this reanalysis possible. 

\par \textbf{Warning:} this reanalysis is my own work. The results will not exactly reproduce the figures or values in Smil (2019). In particular, I  am aware of the following issues with some of the fits:

\begin{itemize}
\item 1.17.2 - no fit available. I am not aware of an easy off-the-shelf way to fit an asymmetrical logistic in R (not a model I have ever used    and not aware of an implementation). I attempted to fit my own specification of model but it was very slow and didn't seem to be converging.
\item 4.13 - the fit fails completely. I think since here I am fitting a logistic but should probably try exponential.
\item 4.19 - Smil fits logistic but I fit an exponential since the process seems in such early stages of growth, but the fit looks bad.
\item 4.28 - ditto the above.
\item 5.11 - the logistic fit looks very poor.
\end{itemize}




