\section*{Bibliography}

This bibliography is taken directly from Smil (2019). References appear exactly as they do there (minus some formatting). \par\par

BP (British Petroleum). 2017. BP Statistical Review of World Energy. London: BP.\par
Ballal, D., and J. Zelina. 2003. Progress in aeroengine technology (1939–2003). Journal of Aircraft 41:43–50.\par
Beaver, P. 1972. A History of Tunnels. Secaucus, NJ: Citadel Press.\par
Buchanan, R. L., et al. 1997. When is simple good enough: A comparison of the Gompertz, Baranyi, and three-phase models for fitting bacterial growth curves. Food Microbiology 14:313–326.\par
CISCO. 2017. The zettabyte era: Trends and analysis. \url{https://webobjects.cdw.com/webobjects/media/pdf/Solutions/Networking/White-Paper-Cisco-The-Zettabyte-Era-Trends-and-Analysis.pdf}.\par
Canalys. 2007. 64 million smart phones shipped worldwide in 2006. \url{https://www.canalys.com/static/press_release/2007/r2007024.pdf}.\par
Daugherty, C. R. 1927. The development of horse-power equipment in the United States. In C. R. Daugherty et al., Power Capacity and Production in the United States. Washington, DC: US Geological Survey, pp. 5–112.\par
Emporis. 2017. Cities with most skyscrapers. \url{https://www.emporis.com/statistics/most-skyscraper-cities-worldwide}.\par
FAO. 2018. Faostat. \url{http://www.fao.org/faostat/en/#data}.\par
GLA (Greater London Authority). 2015. Population Growth in London, 1939–2015. London: GLA.\par
GSMArena. 2017. All mobile phone brands. \url{http://www.gsmarena.com/makers.php3}.\par
Giegling, F., et al., eds. 1964. Chronologisch-thematisches Verzeichnis sämtlicher Tonwerke Wolfgang Amade Mozarts. Wiesbaden: Breitkopf \& Härtel.\par
History of Bridges. 2017. The world’s longest bridge—Danyang–Kunshan Grand Bridge. \url{http://www.historyofbridges.com/famous-bridges/longest-bridge-in-the-world/}.\par
ICAO (International Civil Aviation Organization). 2016. Annual Report 2016. \url{https://www.icao.int/annual-report-2016/Pages/default.aspx}.\par
ICOLD (International Commission on Large Dams). 2017. World Register of Dams. \url{http://www.icold-cigb.net/GB/world_register/world_register_of_dams.asp}.\par
ISC (Internet System Consortium). 2017. ISC Internet domain survey. \url{https://www.isc.org/network/survey/}.\par
Klasing, M. J., and P. Milionis. 2014. Quantifying the evolution of world trade, 1870–1949. Journal of International Economics 92:185–197.\par
Landau, S. B., and C. W. Condit. 1996. Rise of the New York Skyscraper, 1865–1913. New Haven, CT: Yale University Press.\par
Meeker, M. 2017. Internet trends 2017—code conference. \url{http://www.kpcb.com/internet-trends}.\par
Mitchell, B., ed. 1998. International Historical Statistics. London: Palgrave Macmillan.\par
Morrey, C. R. 1978. The Changing Population of the London Boroughs. London: Greater London Council.\par
NBS (National Bureau of Statistics of China). 2000. China Statistical Yearbook 2000. Beijing: NBS.\par
NBS. 2016. China Statistical Yearbook 2016. Beijing: NBS. \url{http://www.stats.gov.cn/tjsj/ndsj/2016/indexeh.htm}.\par
Onoda, S. 2015. Tunnels in Japan. Japan Railway \& Transport Review 66:38–51.\par
PBL (Planbureau voor de Leefomgeving). 2010. Land use data. \url{http://themasites.pbl.nl/tridion/en/themasites/hyde/landusedata/index-2.html}.\par
Pearl, R., and L. J. Reed. 1920. On the rate of growth of the population of the United States since 1790 and its mathematical representation. Proceedings of the National Academy of Sciences of the USA 6:275–288.\par
Reed, H. S., and R. H. Holland. 1919. The growth rate of an annual plant Helianthus. Proceedings of the National Academy of Sciences of the USA 5:135–144.\par
SB (Statistics Bureau, Japan). 1996. Historical Statistics of Japan. \url{http://www.stat.go.jp/english/data/chouki/}.\par
SB. 2017a. Japan Statistical Yearbook. Tokyo: SB. \url{http://www.stat.go.jp/english/data/handbook/pdf/2017all.pdf}.\par
SIA (Semiconductor Industry Association). 2017. 2017 Factbook. \url{http://go.semiconductors.org/2017-sia-factbook-0-0-0}.\par
Schurr, S. H., and B. C. Netschert. 1960. Energy in the American Economy 1850–1975. Baltimore, MD: Johns Hopkins University Press.\par
Schurr, S. H., et al. 1990. Electricity in the American Economy: Agent of Technological Progress. New York: Greenwood Press.\par
Skyscraper Center. 2017. 100 tallest completed buildings in the world by height to architectural top. \url{https://www.skyscrapercenter.com/buildings}.\par
Smil, V. 2001. Enriching the Earth. Cambridge, MA: MIT Press.\par
Smil, V. 2003. Energy at the Crossroads. Cambridge, MA: MIT Press.\par
Smil, V. 2008. Energy in Nature and Society. Cambridge, MA: MIT Press.\par
Smil, V. 2010b. Prime Movers of Globalization. Cambridge, MA: MIT Press.\par
Smil, V. 2013a. Harvesting the Biosphere. Cambridge, MA: MIT Press.\par
Smil, V. 2014b. Making the Modern World. Chichester: Wiley.\par
Smil, V. 2017a. Energy and Civilization. Cambridge, MA: MIT Press.\par
Smil, V. 2017b. Energy Transitions. Santa Barbara, CA: Praeger.\par
TMG (Tokyo Metropolitan Region). 2017. The structure of the Tokyo Metropolitan Government (TMG). \url{http://www.metro.tokyo.jp/ENGLISH/ABOUT/STRUCTURE/structure02.htm}.\par
Taagepera, R. 1978. Size and duration of empires: Growth-decline curves, 3000 to 600 B.C. Social Science Research 7:180–196.\par
Talbert, R. J. A., ed. 2000. Barrington Atlas of the Greek and Roman World. Princeton, NJ: Princeton University Press.\par
The State of Obesity. 2017. Adult obesity in the United States. \url{http://stateofobesity.org/adult-obesity/}.\par
USBC (United States Bureau of the Census). 1975. Historical Statistics of the United States: Colonial Times to 1970. Washington, DC: USBC.\par
USCB. 2016a. Highlights of annual 2015 characteristics of new housing. \url{https://www.census.gov/construction/chars/highlights.html}.\par
USDA. 2017a. Crop production historical track records. \url{http://usda.mannlib.cornell.edu/MannUsda/viewDocumentInfo.do?documentID​=​1593}.\par
USEIA. 2016. Average operating heat rate for selected energy sources. \url{https://www.eia.gov/electricity/annual/html/epa_08_01.html}.\par
USEIA. 2019. U.S. Field Production of Crude Oil. \url{https://www.eia.gov/dnav/pet/hist/LeafHandler.ashx?n​=P​ET&s​=M​ CRFPUS1&f​=​M}.\par
USEPA. 2016b. Light-Duty Vehicle CO2 and Fuel Economy Trends. Washington, DC: USEPA. \url{https://www.epa.gov/fuel-economy-trends/report-tables-and-appendices-co2-and-fuel-economy-trends}.\par
Wilson, A., and J. Boehland. 2005. Small is beautiful: U.S. house size, resource use, and the environment. Journal of Industrial Ecology 9:277–287.\par
World Bank. 2018. DataBank. \url{http://databank.worldbank.org/data/home.aspx}.\par
Zeller, T. 2007. Driving Germany: The Landscape of the German Autobahn, 1930–1970. New York: Berghahn.\par
Zu, C., and H. Li. 2011. Thermodynamic analysis on energy densities of batteries. Energy and Environmental Science 4:2614–2625.\par
